Data for the Ontario Restaurant Closures Experiment

### 2021-02-22 outputs/paper/data_simulation.Rmd

---
title: "Data for the Ontario Restaurant Closures Experiment"
author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
subtitle: "Simulation Methods and Parameterization Research"
abstract: "This document explains how data for the Ontario restaurant closures experiment was simulated, including the research that was used for parameterization and the methods used to randomize data."
thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
bibliography: references.bib
---

@@

@@

@@

takeout_percentage
```
```{r, warning = FALSE}
# Check proportion of RestaurantsTableService
tableserv <- yelp_data %>% 
  select(RestaurantsTableService)
summary(tableserv)
```
```{r, warning = FALSE}
tableserv_percentage <- tableserv %>%
  group_by(RestaurantsTableService) %>% 
  summarize(count = n()) %>%
  mutate(percentage = count/sum(count))

@@

 service_percentage
```
According to Ontario restaurant data from Yelp [@yelp_dataset], approximately 6% of restaurants
offer dine in service, 32.5% offer takeout, and 61.5% offer both.

## Survey 1
```{r, warning = FALSE}
# randomly assign service_provided using ratios above

@@

## Survey 2
```{r, warning = FALSE}
# randomly assign service_provided using ratios above

@@

# Demographic traits of owners

@@

## Survey 1
```{r, warning = FALSE}
# randomly assign disability status using ratios above

@@

## Survey 2
```{r, warning = FALSE}
# randomly assign disability status using ratios above

@@

@@

@@

@@

```{r, warning = FALSE}
# Randomly sample from the scaled F distribution to generate restaurant revenues, and apply a random number around 1 to add variation:

@@

2.4 FTE -> 1.9 FT + 1 PT.

$ 1.9 / (1.9 + 0.5) = 1.9 / 2.4 = 0.79 $

$ 1 / (1.9 + 0.5) = 1 / 2.4 = 0.42 $

## Survey 1
```{r, warning = FALSE}
# Use revenue to generate realistic numbers of employees for restaurants:

@@

```{r, warning = FALSE}
# Randomly select only a subset of all the generated responses to keep, simulating nonresponse:
# Also randomly select columns to delete in partial responses, and delete the data from those rows/columns:

@@

>>>>

---
title: "Data for the Ontario Restaurant Closures Experiment"
author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  bookdown::pdf_document2:
    toc: yes
subtitle: "Simulation Methods and Parameterization Research"
abstract: "This document explains how data for the Ontario restaurant closures experiment was simulated, including the research that was used for parameterization and the methods used to randomize data."
thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
bibliography: references.bib
---

@@

# Introduction

@@

## Research

@@

takeout_percentage
```

```{r, warning = FALSE}
# Check proportion of RestaurantsTableService
tableserv <- yelp_data %>% 
  select(RestaurantsTableService)
summary(tableserv)
```

```{r, warning = FALSE}
tableserv_percentage <- tableserv %>%
  group_by(RestaurantsTableService) %>% 
  summarize(count = n()) %>%
  mutate(percentage = count/sum(count))

@@

 service_percentage
```

According to Ontario restaurant data from Yelp [@yelp_dataset], approximately 6% of restaurants
offer dine in service, 32.5% offer takeout, and 61.5% offer both.

```{r, warning = FALSE}
# randomly assign service_provided using ratios above

@@

```{r, warning = FALSE}
# randomly assign service_provided using ratios above

@@

# Demographic traits of owners: disability

## Research

@@

```{r, warning = FALSE}
# randomly assign disability status using ratios above

@@

```{r, warning = FALSE}
# randomly assign disability status using ratios above

@@

# Demographic traits of owners: racial and ethnic minorities and gender

## Research

@@

## Research into restaurant revenue

@@

## Research into changes in revenue due to closures

@@

```{r, warning = FALSE}
# Randomly sample from the scaled F distribution to generate restaurant revenues, 
# and apply a random number around 1 to add variation:

@@

$1.9 / (1.9 + 0.5) = 1.9 / 2.4 = 0.79$

$1 / (1.9 + 0.5) = 1 / 2.4 = 0.42$

@@

```{r, warning = FALSE}
# Randomly select only a subset of all the generated responses to keep, 
# simulating nonresponse. Also randomly select columns to delete in partial responses, 
# and delete the data from those rows/columns:

@@

# Budget

```{r}
# research for typical budget numbers
restaurants = 2006
survey_total = 2
# https://www.canadapost.ca/cpc/en/business/postal-services/mailing/letter-discounts.page?
indiv_postage = 0.85 
# https://www.ontario.ca/document/your-guide-employment-standards-act-0/minimum-wage
minimum_wage = 14.25 
# https://www.alchemer.com/plans-pricing/small-teams/
management_service = 1300 
average_call_mins = 7
response_rate = .3

# calculate costs
phone_interviewer_cost = 
  round(restaurants * survey_total*response_rate, 2) * average_call_mins / 60 * minimum_wage

postage_cost = (restaurants * 2) * indiv_postage

# save the information in a dataframe
survey_budget <- data.frame(
  Item = c ("Data Management", "Phone Interviewer Wages", "Postage", "TOTAL"),
  Cost = c (management_service, 
            phone_interviewer_cost, 
            postage_cost, 
            sum(management_service, phone_interviewer_cost, postage_cost)),
  Description = c ("Online survey management account fees",
                   "1,203 calls (7 minutes on average) at $14.25/hr",
                   "4,012 mailers at $0.85/ea",
                   "")
)

write_csv(survey_budget, here("outputs/data/survey_budget.csv"))
```
